---
title: "Plotly"
author: "Zuzu"
date: "November 1, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset

```{r}
library(readr)
library(janitor)
library(stringr)
library(forcats)
library(viridis)
library(plotly)
```

```{r}
airbnb = read_csv("./data/nyc_airbnb.zip") %>%
  clean_names() %>%
  rename(boro = neighbourhood_group) %>%
  filter(boro == "Manhattan", room_type =="Entire home/apt", price > 100 & price < 400)
```

### Plotly Scatterplot

plotly::plot_ly: initiate plotly visualization

main thing: put the aesthetics

mode = marker: give me a scatterplot where individual point shows as a point

color = ~price:plot price use different color

text = : the text you want to show when you scolling on the point in the graph 

"\nRating": the "\n" means creating a new line 

```{r}
library(tidyverse)
airbnb %>% 
  mutate(hover_text = str_c("Price: $", price,"\nRating:", review_scores_location / 2)) %>%
  plot_ly(x = ~longitude, y = ~latitude, color = ~price, text = ~hover_text, type = "scatter", mode = "marker", alpha = 0.5)
```

### Plotly boxplot

color = ~neighbourhood + colors = "Set2": put color for each neighbourhood

```{r}
airbnb %>%
  mutate(neighbourhood = forcats::fct_reorder(neighbourhood, price)) %>%
  plot_ly(x = ~neighbourhood, y = ~price, color = ~neighbourhood, colors = "Set2", type = "box") 
```


### Plotly barchart

```{r}
airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar")
```


### ggplotly

```{r}
library(ggplot2)
scatter_ggplot = airbnb %>%
  ggplot(aes(x = longitude, y = latitude, color = price)) +
  geom_point(alpha = 0.25) +
  scale_color_viridis() +
  coord_cartesian() +
  theme_classic()

ggplotly(scatter_ggplot)
```



